Efficient Coalition Formation for Web Services

### 2013-03-10 papers/coalition/coalition.tex
Changes

As future work, we would like to perform more analytical and theoretical work on the convexity condition for the characteristic function on web service applications. A future research direction includes working on compact or succinct representation of our service model to reduce the input complexity of cooperative game stability and fairness and membership checking solutions. From web service aspect the work can be extended to consider web service compositions where a group of web services having different set of skills cooperate to perform composite tasks.

>>>>

As future work, we would like to perform more analytical and theoretical work on the convexity condition for the characteristic function on web service applications. It is possible to work on compact or succinct representation of our service model (i.e. a graph representation) to reduce the input complexity and solution concepts of cooperative game and membership checking algorithms. From web service aspect, the work can be extended to consider web service compositions where a group of web services having different set of skills cooperate to perform composite tasks. Also bargaining theory from cooperating game theory concepts can be used in our scenario. The web services would stay and join communities as they wish, however, they would resolve the instability and unfairness issues by side payments.
